Leveraging Diversity to Find Bugs in JavaScript Engines

### 2019-02-13 paper/paper.tex
pass on abstract and intro

JavaScript (\js{}) is one of the most popular programming languages
today~\cite{stackify,redmonk-javascript}, with penetration in various software development segments including, web, mobile,
and, more recently, the Internet of
Things~(IoT)~\cite{simply-technologies}. The interest of the community
for the language encourages constant improvements in its specification~\cite{ecmas262-spec}. It is natural to expect that such improvements
lead to sensible changes in engine implementations~\cite{kangax}. Even small
changes can have high practical impact. For example, in October 2014 a
new attribute added to Array objects resulted in the MS Outlook
Calendar web app, which is built in \js{}, failing under
Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.

Finding bugs in \js\ engines is an important problem given the range
of applications that could be affected with those bugs. It is also
challenging.  Specifications are intentionally incomplete as to enable
development flexibility. In addition, they evolve frequently to
accommodate the pressing demands from
developers~\cite{ecmas262-spec-repo}. An official conformance test
suite exists for \js~\cite{tc39-github}, but, naturally, many test
scenarios are not covered in the suite. In addition, we noticed that a
significant fraction (5 to 15\%) of the tests constantly fail on the
most popular engines, reflecting the struggle of developers in keeping
up with the pace of spec evolution (see Table~\ref{tab:test262}).

%% WHAT WE DID
This paper reports on a study we ran to evaluate the importance of
diversity in finding bugs on JavaScript engines. We evaluated
effectiveness of two complementary diversity-aware testing
techniques. \emph{Test transplantation} leverages diversity of test
cases to find bugs. It evaluates the effects that running \js{} test
files from a given engine have in detecting bugs in other engines. The
intuition is that developers design test cases with different
objectives in mind. Replaying these tests, written for a given engine,
in a different engine may reveal unanticipated
problems. \emph{Cross-engine differential testing} leverages diversity of engine implementations to find
bugs. More precisely, this technique fuzzes existing test
inputs~\cite{fuzz-testing-history} and then compares the output
produced by different engines using a differential oracle. The
intuition is that similar inputs to those already tested may reveal
problems. Our study measures the ability of these techniques in
finding bugs and the impact of false positives, which
can arise in both testing scenarios.

@@

\emph{Related Ideas.}  It is worth noting that Differential
Testing~\cite{Brumley-etal-ss07} (DT) has been applied in a variety of
contexts to find
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
It has shown to be specially practical in scenarios where the
observation of difference gives a strong signal of a real problem. For
example, Mozilla runs JS files\footnote{These files are created with
  the grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
  ``compare\_jit'' from funfuzz.} against different configurations of
a given build of their \smonkey\ engine (\eg{}, trying to enable or
not eager JIT compilation). A positive aspect of the approach is that
it can be fully automated. As the same engine is used, the outcomes of
the test in both configurations are expected to be identical. The
Mozilla team uses this approach since 2002; they have been able to
find over 270 bugs since then~\cite{jsfunfuzz-at-mozilla}, including
security bugs. Cross-engine differential testing, in contrast, has not
been widely popularized. One possible reason is that it is still not
practical to fully automate the technique. In contrast to other
applications of differential testing, a number of legitimate reasons
exist, other than a bug, for a test execution to manifest discrepancy
(see Tables~\ref{fig:piecharts-transplantation} and
~\ref{tab:false-positives}). \Mar{rewrite. too vague.}\Fix{This paper
  evaluates the potential benefits of diversity techniques, including
  DT. It provides data to support or not the decision for automation
  of these techniques.}

@@

\emph{Results.}~We considered engines from four major players--Apple,
Google, Microsoft, and Mozilla. Our results indicate that both
techniques revealed several bugs, most of which confirmed by
developers. Test transplantation revealed \noBugsTransplantation{}
bugs (of which, \noBugsTransplantationConfirmed{} were confirmed and
\noBugsTransplantationFixed{} were fixed) whereas differential testing
revealed \noBugsDifferentialTesting{} bugs (of which,
\noBugsDifferentialTestingConfirmed{} were confirmed and
\noBugsDifferentialTestingFixed{} were fixed). Furthermore, results
indicate that most of these bugs affected two engines--Apple's \jsc{}
and Microsoft's \chakra{}.  We reported \noBugsBugsReportedGoogle{}
bugs in Google \veight{} (\noBugsBugsConfirmedGoogle{} confirmed) and
none in Mozilla's \smonkey{}.

\emph{Key Findings.}~Results indicate that both techniques were
successful at finding bugs. Overall, test transplantation demanded
less effort compared to differential testing per bug
found.\Fix{redundant with the sentences that follow...check} Although
our experience indicates that more research needs be done to automate
parts of the inspection process, our results show that exploring
diversity is a valuable help to find bugs in JavaScript
engines. \Fix{copied from ICSE meta-review $\rightarrow$}The key
findings could include, e.g.: - Not only multiple different
implementations can be leveraged in differential testing, also
differences in test suites can be important.  - Even for problems with
fairly clear specifications, as here for a programming language and
how it is to be executed, there is likely to be (a lot of) variation
between different implementations.  - Differential testing is feasible
on real, complex, widely used pieces of software.

%% LIST OF CONTRIBUTIONS
\emph{Contributions.}~This paper contributes the following:
\begin{itemize}
  \item We ran a comprehensive study to analyze the effectiveness of
    simple diversity-aware techniques to find functional bugs in
     popular \js\ engines;

  \item We reported a total of \totalBugsReported{} bugs on these
    engines. Of these, \totalBugsConfirmed{} bug reported were confirmed and
    \totalBugsFixed{} were fixed;

  %% \item We offered insights on how to reduce cost of analyzing
  %%   warnings reported by diversity-aware techniques and make the
  %%   approach more practical.

  \item We made our testing infrastructure, results, and experimental
    scripts available to the public. (upon request for anonymity.)

\end{itemize}

>>>>

JavaScript (\js{}) is one of the most popular programming languages
today~\cite{stackify,redmonk-javascript}, with penetration in various software development segments including, web, mobile,
and, more recently, the Internet of
Things~(IoT)~\cite{simply-technologies}. The interest of the community
for the language encourages constant improvements in its specification~\cite{ecmas262-spec}. It is natural to expect that such improvements
lead to sensible changes in engine implementations~\cite{kangax}. Even small
changes can have high practical impact. For example, in October 2014 a
new attribute added to Array objects resulted in the MS Outlook
Calendar web app, which is built in \js{}, to fail under 
Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.

Finding bugs in \js\ engines is an important problem given the range
of applications that could be affected with those bugs. It is also
challenging.  Specifications are intentionally incomplete as to enable
development flexibility. In addition, they evolve frequently to
accommodate the pressing demands from
developers~\cite{ecmas262-spec-repo}. An official conformance test
suite exists for \js~\cite{tc39-github}, but, naturally, many test
scenarios are not covered in the suite. In addition, we noticed that a
significant fraction (5 to 15\%) of the tests fail regularly in the
most popular engines, reflecting the struggle of developers in keeping
up with the pace of spec evolution (see Table~\ref{tab:test262}).

%% WHAT WE DID
This paper reports on a study we ran to evaluate the importance of
diversity to find bugs in JavaScript engines. We evaluated
effectiveness of two complementary diversity-aware testing
techniques.

\begin{itemize}

\item \emph{Test transplantation} leverages diversity of test cases to
  find bugs. It evaluates the effects that running test files from a
  given engine have in detecting bugs in other engines. The intuition
  is that developers design test cases with different objectives in
  mind. As such, replaying these tests in different engines could
  reveal unanticipated problems.

\item \emph{Cross-engine differential testing} leverages diversity of engine implementations to find
bugs. More precisely, this technique fuzzes existing test
inputs~\cite{fuzz-testing-history} and then compares the output
produced by different engines using a differential oracle. The
intuition is that similar inputs to those already tested may reveal
problems.
\end{itemize}

Our study measures the ability of these techniques in finding bugs and
the impact of false positives, which can arise in both testing
scenarios, on the practicality of the approach.

@@

\emph{Related Ideas.}\Mar{Summarize Test Transplantation.} It is worth
noting that Differential Testing~\cite{Brumley-etal-ss07} (DT) has
been applied in a variety of contexts to find
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
It has shown to be specially practical in scenarios where the
observation of difference gives a strong signal of a real problem. For
example, Mozilla runs JS files\footnote{These files are created with
  the grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
  ``compare\_jit'' from funfuzz.} against different configurations of
a given build of their \smonkey\ engine (\eg{}, trying to enable or
not eager JIT compilation). A positive aspect of the approach is that
it can be fully automated---as only one engine is used, the outcomes
of the test in both configurations are expected to be identical. The
Mozilla team uses this approach since 2002; they have been able to
find over 270 bugs since then~\cite{jsfunfuzz-at-mozilla}, including
security bugs. Cross-engine differential testing, in contrast, has not
been widely popularized. One possible reason is that it is still not
practical to fully automate the technique. In contrast to other
applications of differential testing, a number of legitimate reasons
exist, other than a bug, for a test execution to manifest discrepancy
(see Tables~\ref{fig:piecharts-transplantation} and
~\ref{tab:false-positives}). To sum, variations of these ideas have
been explored before in different contexts.  The goal of the paper is
to assess the ability of these techniques aforementioned in finding
bugs on \javascript\ engines.

%% This paper evaluates the benefits of
%% test case diversity and engine diversity in finding bugs on
%% \javascript\ engines.

@@

\emph{Results.}~We considered engines from four major players--Apple,
Google, Microsoft, and Mozilla. Our results indicate that both
techniques revealed several bugs, most of which confirmed by
developers. Test transplantation revealed \noBugsTransplantation{}
bugs (of which, \noBugsTransplantationConfirmed{} were confirmed and
\noBugsTransplantationFixed{} were fixed) whereas differential testing
revealed \noBugsDifferentialTesting{} bugs (of which,
\noBugsDifferentialTestingConfirmed{} were confirmed and
\noBugsDifferentialTestingFixed{} were fixed). Furthermore, results
indicate that most of these bugs affected two engines--Apple's \jsc{}
and Microsoft's \chakra{}.  We reported \noBugsBugsReportedGoogle{}
bugs in Google \veight{} (\noBugsBugsConfirmedGoogle{} confirmed) and
none in Mozilla's \smonkey{}. Overall, results indicate that both
techniques were successful at finding bugs. Considering cost per bug
found, test transplantation demanded less effort--from the developers
who inspected the alarms---compared to differential testing.

\emph{Key Findings.}~1) Not only multiple different implementations
can be leveraged in differential testing, but differences in test
suites can also be important. 2) Even for problems with fairly clear
specifications, as in \javascript{}, there is likely to be (a lot of)
variation between different implementations. 3) Differential testing
is feasible on real, complex, widely used pieces of software. 4) More
research needs be done to automate parts of the inspection process as
to reduce false alarms and prioritize alarms for inspection.

%% LIST OF CONTRIBUTIONS
\emph{Contributions.}~This paper contributes the following: 1)~A
comprehensive study to analyze the effectiveness of diversity-aware
techniques to find functional bugs in popular \javascript\ engines.
2)~A number of bugs found and fixed. We reported a total of
\totalBugsReported{} bugs. Of these, \totalBugsConfirmed{} bugs were
confirmed and \totalBugsFixed{} bugs were fixed. 3)~An infrastructure
for diversity-aware testing. We made our testing infrastructure,
results, and experimental scripts available to the public. (upon
request for anonymity.)

To sum, the paper provides initial, yet strong evidence that exploring
diversity is a valuable help to find bugs in JavaScript engines and
should be encouraged.
